IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
fig for node

This issue of performance and JavaScript isolation is not unique to
our work. 
%
In particular, browser layout engines rely on the isolation of content
from different origins (e.g., two iframes of different origins) to
implement the \emph{same-origin policy}.
%
Since creating an OS thread for each iframe is expensive, both V8 and
SpiderMonkey provide a means for running JavaScript code in isolation,
on disjoint sub-heaps of the same OS thread.
%
In V8 this unit of isolation is called a \emph{context}~\tocite{}, in
SpiderMonkey, it called a \emph{compartment}~\tocite{}.
%
(We will use these terms and ``task'' interchangeably.)
%
Each context/compartment is associated with a global object, which
implements the JavaScript standard library (e.g., \verb|Object|,
\verb|Array|, etc.).
%
It is this global object that is extended with feature such as the
DOM and filesystem.

@@

We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by |targetLangJS|).
%
The direct approach for implementing the embedded language |specLangJS roundrobinf| is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \verb|getElementById|, by attaching them to
the global JS object.
%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

Since this implementation approach relies on multiple runtimes of the
language, sending arbitrary objects between tasks can result in
unexpected behavior, e.g., when the object contains references.
%
As discussed in Section~\ref{sec:concrete}, we need to restrict |send|
to expressions that can be marshalled as strings, i.e., structurally
clonable objects.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

>>>>

However, this issue of performance and JavaScript isolation is not
unique to our work. 
%
In particular, browser layout engines rely on the isolation of content
from different origins (e.g., two iframes of different origins) to
implement the \emph{same-origin policy}.
%
Since creating an OS thread for each iframe is expensive, both V8 and
SpiderMonkey provide a means for running JavaScript code in isolation,
on disjoint sub-heaps of the same OS thread.
%
In V8, this unit of isolation is called a \emph{context}~\tocite{}, in
SpiderMonkey, it called a \emph{compartment}~\tocite{}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
(Gecko and Node.js expose features such as the DOM and
filesystem by extending this global object.)
%

We leverage contexts to implement |specLangJS seqf| for Node.js.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library and our IFC primitives (|send|, |sandbox|, etc.).
%
In turn, these tasks can create new tasks with |sandbox|.
%
Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
the global object corresponding to the standard JavaScript library and
our IFC primitives.

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks.}
\end{figure}
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
While V8 provides a means for sharing objects between contexts that
share a security token (in the case of Blink this is used by pages of
the same origin), our API (conservatively) restricts the kinds of
messages that can be exchanged.
%
More concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
However, our implementation is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

@@

We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).
